Behavior Driven Development in Haskell

### 2012-05-30 paper.tex
Fix grammar issue
Put evidence into footnote

Haddock has markup support for code blocks~\cite{haddock}.  And it is widely used to
include properties and examples in documentation.
For instance, some packages, including {\tt containers}, {\tt filepath}, 
{\tt bytestring} and {\tt text}, adopt this style.
Here is an example from the first one.

>>>>

Haddock has markup support for code blocks, and they are widely used
to include properties and examples into documentation\footnote{
See e.g. the documentation of
{\tt containers},
{\tt filepath},
{\tt bytestring} or
{\tt text}}.
Here is an example from the {\tt containers} package.
